Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-30 paper.tex
Edit Trading Model

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\

@@

\section{System Architecture}
\subsection{Participants}
There are four major roles in the decentralized data marketplace (Figure \ref{fig:system_design}).

@@

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power. Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a new Product Contract, which specifies details about products, and upload this product to the IPFS (InterPlanetary File System)\cite{IPFS}. Also the broker certifies the session key which is used for symmetric encryption for streaming data encryption and decryption. Then the broker provides the matching service for data provider’s products and consumer’s queries. After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{system_design}
	\caption{System Design.}
	\label{fig:system_design}
\end{figure}

@@

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications.

@@

Brokers certify session keys as well. However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. Figure \ref{fig:key_certification} shows the certification process. When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key to the broker. The broker signs the message and returns the signature to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer. After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature. Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.

>>>>

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\

@@

\section{System Architecture}
\subsection{Participants}
There are four major roles in the decentralized data marketplace.

@@

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power. Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a new Product Contract, which specifies details about products, and upload this product to a decentralized storage system\cite{IPFS}. Also the broker certifies the session key which is used for symmetric encryption for streaming data encryption and decryption. Then the broker provides the matching service for data provider’s products and consumer’s queries. After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.

@@

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

@@

Brokers certify session keys as well. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers. However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. Figure \ref{fig:key_certification} shows the certification process. When a data provider asks a broker to ceritfy new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key $Blind(k)$ to the broker. The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer. After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$. Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.
